Draft Exploration

### 2020-04-06 draft_exploration.Rmd
fixed WAR data to include pitching and hitting

```{r, include=FALSE}
war <- read_csv("data/war.csv")
```

@@

war_joined <- war %>%
  group_by(mlb_ID) %>%
  summarize(g = sum(G),
            war = sum(as.numeric(WAR)))

@@

@@

mlb_percentile_signed <- function(round = 20, startyear = 1990, endyear = 2010) {

@@

# 27.3% of signed top 20 round high school picks from 1990-2010 have made it to MLB

@@

```{r, echo=FALSE}
top_20_unsigned_total <- master %>%
  filter(source == "H" & signed == "N" & draft_numb == 1) %>%
  filter(draft_round <= 20 & year >= 1990 & year <= 2010) %>%
  count() %>%
  pull(n)

top_20_unsigned_mlb <- master %>%
  filter(source == "H" & signed == "N" & draft_numb == 1 & high_level == "MLB") %>%
  filter(draft_round <= 20 & year >= 1990 & year <= 2010) %>%
  count() %>%
  pull(n)

mlb_percentile_20u <- top_20_unsigned_mlb / top_20_unsigned_total

# 22.7% of unsigned top 20 round high school picks from 1990-2010 have made it to MLB

>>>>

# combining hitting and pitching war for each player-season

batting_war <- read_csv("data/bat_war.csv") %>%
  mutate(bat_war = as.numeric(WAR))

pitching_war <- read_csv("data/pitch_war.csv") %>%
  mutate(pitch_war = as.numeric(WAR)) %>%
  select(mlb_ID, year_ID, pitch_war)

war <- batting_war %>%
  full_join(pitching_war, by = c("mlb_ID", "year_ID")) %>%
  mutate(war = bat_war + pitch_war)
```

@@

war_joined <- war %>%
  group_by(mlb_ID) %>%
  summarize(g = sum(G),
            war = sum(as.numeric(war)))

@@

```{r}

# adding in age of MLB debut season

debut <- war %>%
  group_by(mlb_ID) %>%
  summarize(debut = min(age))

master <- master %>%
  left_join(debut, by = c("mlbid" = "mlb_ID"))
```

@@

mlb_percentile_signed <- function(round = 20, startyear = 1990, endyear = 2011) {

@@

mlb_percentile_signed(round = 20, startyear = 1990, endyear = 2011)
# 27.3% of signed top 20 round high school picks from 1990-2010 have made it to MLB

@@

mlb_percentile_unsigned <- function(round = 20, startyear = 1990, endyear = 2011) {

top_20_unsigned_total <- master %>%
  filter(source == "H" & signed == "N" & draft_numb == 1) %>%
  filter(draft_round <= round & year >= startyear & year <= endyear) %>%
  count() %>%
  pull(n)

top_20_unsigned_mlb <- master %>%
  filter(source == "H" & signed == "N" & draft_numb == 1 & high_level == "MLB") %>%
  filter(draft_round <= round & year >= startyear & year <= endyear) %>%
  count() %>%
  pull(n)

top_20_unsigned_mlb / top_20_unsigned_total

}
# 22.7% of unsigned top 20 round high school picks from 1990-2010 have made it to MLB

mlb_percentile_unsigned(round = 20, startyear = 1990, endyear = 2011)
```
